---
title: "KeyATM"
author: "Alvaro millan"
date: "2025-06-06"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r}
#library(text)
library(dplyr)
library(keyATM)
library(quanteda)
library(quanteda.textstats)
library(ggplot2)
library(lubridate)
```

```{r}
final_df <- read.csv("C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/Final_df.csv")
```

```{r}
# Prepare the dataframe for topic modelling
topic_modelling_df <- final_df %>%
  select(cleaned_speeches_no_postagging_expanded, Year, Income.Level, ISO.Code) %>%
  rename(text = cleaned_speeches_no_postagging_expanded)
```


# Check for bigrams MANUALLY

```{r}
bigrams <- read.csv("C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/bigrams.csv")
```

```{r}
bigrams = c("climate change", "global warming", "global warm","cap and trade", "paris accord", "emissions trading", "global average temperature", "kyoto protocol", "climate resilience", "carbon dioxide", "climate politics", "framework convention on climate change", "ball roadmap", "greenhouse gas", "greenhouse effect", "climate mitigation", "climate action", "temperature", "extreme weather", "global environmental change", "global environment", "global environmental" ,"climate variability", "low carbon", "renewable energy", "carbon emission", "climate pollutant", "climate pollutants", "carbon tax", "carbon footprint", "carbon neutrality", "net-zero", "net zero", "climate crisis", "climate summit", "climate catastrophe", "climate justice", "climate emergency", "climate funding", "climate fund", "climate financing", "climate finance","climate peace", "climate agreement", "climate security", "climate ambition", "climate issue", "climate impact", "climate conference", "climate event", "climate challenge", "climate trust", "climate negotiation", "climate catastrophe", "climate risk", "climate goal", "climate change-related", "climate regime", "climate resilient", "climate policy", "carbon market", "carbon sink", "green climate", "green economy", "emission reduction", "emissions reduction", "carbon neutral", "carbon sink", "ozone layer", "emissions trading scheme")

tokenized_docs <- strsplit(topic_modelling_df$text, " ")

# Convert your tokenized list to a quanteda tokens object
tokens_obj <- tokens(as.list(tokenized_docs)) 


tokens_obj <- tokens_compound(tokens_obj, phrase(bigrams))

# 6. Create DFM and trim
dfm_obj <- dfm(tokens_obj) %>%
  dfm_trim(min_termfreq = 1, min_docfreq = 1)

# 7. Remove empty documents (critical for KeyATM)
dfm_obj <- dfm_subset(dfm_obj, ntoken(dfm_obj) > 0)

kept_docs <- docnames(dfm_obj)  # These are "text1", "text2", etc.

# 2. Create matching IDs in your original data
topic_modelling_df <- topic_modelling_df %>%
  mutate(doc_id = paste0("text", row_number()))  # Create matching IDs

docvars <- topic_modelling_df %>%
  filter(doc_id %in% kept_docs) %>%           # Keep only docs that exist in DFM
  arrange(match(doc_id, kept_docs)) %>%       # Put in same order as DFM
  transmute(
    Year = as.numeric(Year),
    Income.Group = factor(
      Income.Level,
      levels = c(1, 2, 3, 4),
      labels = c("Low", "Lower-Middle", "Upper-Middle", "High") # first level ("Before2015") is treated as the baseline dummy variable
    ),
    Year_std = as.vector(scale(Year))
  ) %>%
  mutate(
    Period = factor(
      ifelse(Year < 2015, "Before2015", "After2015"), 
      levels = c("Before2015", "After2015")
    )
  )

# Ensure docvars rows match dfm_obj EXACTLY
stopifnot(nrow(docvars) == ndoc(dfm_obj))

# 3. First attach docvars to the DFM (proper quanteda method)
docvars(dfm_obj) <- docvars  # Attach your prepared metadata

# 4. Convert to keyATM format (preserving docvars)
keyATM_docs <- keyATM_read(texts = dfm_obj)
```


```{r}
keywords <- list(
  Climate = c("climate_change", "global_warming", "global_warm","cap_and_trade", "paris_accord", "emissions_trading", "global_average_temperature", "kyoto_protocol", "climate_resilience", "carbon_dioxide", "climate_politics", "framework_convention_on_climate_change", "framework_convention_climate_change", "ball_roadmap", "greenhouse_gas", "greenhouse_effect", "climate_mitigation", "climate_action", "emissions", "temperature", "extreme weather", "global environmental_change", "global_environment", "global_environmental" ,"climate_variability", "low_carbon", "renewable_energy", "carbon_emission", "climate_pollutant", "climate_pollutants", "carbon_tax", "carbon_footprint", "carbon_neutrality", "net_-_zero", "net_zero", "climate_crisis", "climate_summit", "climate_catastrophe", "climate_justice", "climate_emergency", "climate_funding", "climate_fund", "climate_financing", "climate_finance","climate_peace", "climate_agreement", "climate_security", "climate_ambition", "climate_issue", "climate_impact", "climate_conference", "climate_event", "climate_challenge", "climate_trust", "climate_negotiation", "climate_catastrophe", "climate_risk", "climate_goal", "climate_change-related", "climate_regime", "climate_resilient", "climate_policy", "carbon_market", "carbon_sink", "green_climate", "green_economy", "emission_reduction", "emissions_reduction", "carbon_neutral", "carbon_sink", "ozone_layer", "emissions_trading_scheme", "ghg", "ghge", "co2", "ipcc")
)
```

```{r}
climate_keywords_dict <- list(
  
  # 1. Climate Science & Impacts
  science_impacts = c(
    "climate_change", "global_warm", "global_warming", "global_average_temperature",
        "climate_variability", "extreme_weather", "climate_impact",
        "greenhouse_effect", "temperature", "climate_catastrophe",
        "climate_risk", "ozone_layer", "global_environmental_change",
        "global_environmental", "global_environment", 
        "climate_change-related", "climate_risk"
  ),
  
  # 2. Policy & Agreements
  policy_agreements = c(
    "paris_accord", "kyoto_protocol", "unfccc", "climate_policy",
        "framework_convention_on_climate_change", "framework_convention_climate_change",
        "climate_agreement", "climate_regime", "climate_negotiation", "climate_ambition",
        "climate_security", "ball_roadmap", "ipcc"
  ),
  
  # 3. Carbon & Emissions
  carbon_emissions = c(
    "carbon_dioxide", "co2", "carbon_emission", "carbon_tax",
        "carbon_footprint", "carbon_neutrality", "carbon_neutral",
        "carbon_market", "carbon_sink", "low_carbon", "emissions",
        "emission_reduction", "emissions_reduction", "ghg", "ghge",
        "climate_pollutant", "climate_pollutants", "carbon_neutral",
        "greenhouse_gas"
  ),
  
  # 4. Climate Action & Solutions
  action_solutions = c(
     "climate_action", "climate_mitigation", "renewable_energy",
        "climate_resilience", "climate_resilient", "green_economy",
        "climate_funding", "climate_fund", "climate_financing", "climate_finance",
        "net-zero", "net_zero", "green_climate", "cap_and_trade",
        "emissions_trading scheme", "emissions_trading"
  ),
  
  # 5. Sociopolitical Climate Issues
  sociopolitical = c(
    "climate_justice", "climate_emergency", "climate_crisis",
        "climate_summit", "climate_politics", "climate_peace",
        "climate_challenge", "climate_goal", "climate_issue",
        "climate_event", "climate_conference", "climate_trust"
  )
)

```


```{r}
# 4. Now run keyATM with covariates
#model_dict <- keyATM(
#  docs = keyATM_docs,
#  keywords = climate_keywords_dict,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
#    covariates_formula = ~ Income.Group + Period,
#    covariates_data = docvars(dfm_obj),  # Pull from attached docvars
#    standardize = "none"
#  ), 
#   options = list(seed = 123)
#)
```


```{r}
# 4. Now run keyATM with covariates
#model <- keyATM(
#  docs = keyATM_docs,
#  keywords = keywords,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
#    #covariates_formula = ~ Income.Group * Year_std,
#    covariates_formula = ~ Income.Group + Period,
#    covariates_data = docvars(dfm_obj),  # Pull from attached docvars
#    standardize = "none"
#  ), 
#   options = list(seed = 123)
#)
```


```{r}
#saveRDS(model, file = "C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model.rds")

#saveRDS(model_dict, file = "C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_dict.rds")
```

```{r}
# Choose whicever u want to test for, the one that is suborganized into different topics, keyATM_model_dict.rds, or the ones that is simple keyATM_model.rds

model <- readRDS("C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model.rds")

#model <- readRDS("C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_dict.rds")
```


2
** The by_strata_DocTopic() function can display the marginal posterior means of document-topic distributions for each value of (discrete) covariates. **  

```{r}
strata_topic <- by_strata_DocTopic(
  model, by_var = "PeriodAfter2015",
  labels = c("1990_2014", "2015_24")
)
```


** The figure shows the marginal posterior means of document-topic distributions and the 90% credible intervals of them for each value of covariates. ** 


```{r}
#fig_doctopic <- plot(strata_topic, var_name = "Period", show_topic = c(1,2,3,4,5))
fig_doctopic <- plot(strata_topic, var_name = "Period", show_topic = c(1))
fig_doctopic
```

** We can visualize results by covariate with by = "covariate" argument. The plot below combines two panels in the previous plot and display in the same panel. ** 

```{r}
# run only if you have selected the keyATM_model_dict.rds
key_viz <- visualize_keywords(
  docs = keyATM_docs,
  keywords = climate_keywords_dict,
  prune = TRUE, # or even Inf to show everything
  label_size = 2.5
)

viz_data_filtered <- values_fig(key_viz)


climate_keyword_plot <- viz_data_filtered %>%
  filter(`Proportion(%)` > 0) %>%
  ggplot(aes(x = reorder(Word, `Proportion(%)`), y = `Proportion(%)`, fill = Topic)) +
  geom_col() +
  coord_flip() +
  labs(x = "Keyword", y = "Proportion (%)", fill = "Topic Group") +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA)
  )


climate_keyword_plot
```

** Using the output of the keyATM, we can calculate 90% credible intervals of the differences in the mean of document-topic distribution. **

** Since we set the years prior to 2015 dummy as the baseline when constructing factor for this variable, the comparison is the relative increase or decrease from the years prior to 2015 to the years from 2015 to 2024. 

```{r}
theta1 <- strata_topic$theta[[1]]  # Topic proportions for 1990–2014
theta2 <- strata_topic$theta[[2]]  # Topic proportions for 2015–2024
#theta_diff <- theta2[, c(1,2,3,4,5)] - theta1[, c(1,2,3,4,5)]  # focus on two topics
theta_diff <- theta2[, c(1)] - theta1[, c(1)]
theta_diff_quantile <- quantile(theta_diff, c(0.05, 0.5, 0.95)) # Difference in topic 1
#theta_diff_quantile <- apply(theta_diff, 2, quantile, probs = c(0.05, 0.5, 0.95)) # prevalence Lower bound of the 90% credible interval. Median of the difference (i.e. central estimate). Upper bound of the 90% credible interval.
# By how much did the average prevalence of topic 1 (Climate) change between 1990–2014 and 2015–2024? 
theta_diff_quantile
```

* This topic became significantly more prevalent after 2015 — with high certainty. * 

*Furthermore, we can use the predict() function to get the predicted mean of the document-topic distribution for three party categories.*


```{r}
get_strata_estimates <- function(model, var, label) {
  strata <- by_strata_DocTopic(model, by_var = var, labels = c(paste0("Non-", label), label))
  summary(strata)[[label]]
}

est_high      <- get_strata_estimates(model, "Income.GroupHigh", "High")
est_upp_mid   <- get_strata_estimates(model, "Income.GroupUpper-Middle", "Upper-Middle")
est_low_mid   <- get_strata_estimates(model, "Income.GroupLower-Middle", "Lower-Middle")


new_data <- covariates_get(model)

new_data[, "Income.GroupHigh"] <- 0
new_data[, "Income.GroupUpper-Middle"] <- 0
new_data[, "Income.GroupLower-Middle"] <- 0
pred <- predict(model, new_data, label = "Low")

res <- bind_rows(est_high, est_upp_mid, est_low_mid, pred) %>%
          filter(TopicID %in% 1)

#res <- bind_rows(est_high, est_upp_mid, est_low_mid, pred) %>%
          #filter(TopicID %in% c(1, 2, 3, 4, 5))
labels <- unique(res$label)

# The mean topic prevalence (theta) for Topic 1 across income groups. 
# Error bars show 90% credible intervals.

library(ggplot2)
ggplot(res, aes(x = label, ymin = Lower, ymax = Upper, group = Topic)) +
  geom_errorbar(width = 0.1) +
  coord_flip() +
  facet_wrap(~Topic) +
  geom_point(aes(x = label, y = Point)) +
  scale_x_discrete(limits = rev(labels)) +
  xlab("Income Group") +
  ylab(expression(paste("Mean of ", theta))) +
  theme_bw()

# θ (theta) represents the mean document-topic distribution — specifically, the average proportion of a document that is about Topic 1 ("Climate") for each income group
```
* The average prevalence (θ) of this topic in UN speeches, broken down by income group. *

* All income groups discuss "Climate" relatively equally. * 
* Low income group they discuss it in average way less * 

*WHAT ABOUT ADDING A TIME THING 2015 ONWARDS* 


```{r }
#docvars_2 <- topic_modelling_df %>%
#  filter(doc_id %in% kept_docs) %>%
#  arrange(match(doc_id, kept_docs)) %>%
#  transmute(
#    Year = as.numeric(Year),
#    Income.Group = factor(
#      Income.Level,
#      levels = c(1, 2, 3, 4),
#      labels = c("Low", "Lower-Middle", "Upper-Middle", "High")
#    ),
#    Period = factor(
#      ifelse(Year < 2015, "Before2015", "After2015"),
#      levels = c("Before2015", "After2015")
#    ),
#    GroupPeriod = paste0(Income.Group, "_", Period),
#    Year_std = as.vector(scale(Year))
#  )

# Attach docvars to DFM
#stopifnot(nrow(docvars_2) == ndoc(dfm_obj))
#docvars(dfm_obj) <- docvars_2

# Convert to keyATM format
#keyATM_docs <- keyATM_read(texts = dfm_obj)

# Fit the keyATM model
#model_2 <- keyATM(
#  docs = keyATM_docs,
#  keywords = climate_keywords_dict,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
#    covariates_formula = ~ GroupPeriod,
#    covariates_data = docvars(dfm_obj),
#    standardize = "none"
#  ),
#  options = list(seed = 123)
#)
```

```{r}
# Save model
#saveRDS(model_2, file = "C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time2015_dict.rds")
```

```{r}
model_2 <- readRDS("C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time2015_dict.rds")
```



```{r}
est_G1 <- get_strata_estimates(model_2, "GroupPeriodHigh_Before2015", "High_Before2015")

est_G3 <- get_strata_estimates(model_2, "GroupPeriodUpper-Middle_Before2015", "Upper-Middle_Before2015")
est_G4 <- get_strata_estimates(model_2, "GroupPeriodUpper-Middle_After2015", "Upper-Middle_After2015")

est_G5 <- get_strata_estimates(model_2, "GroupPeriodLower-Middle_Before2015", "Lower-Middle_Before2015")
est_G6 <- get_strata_estimates(model_2, "GroupPeriodLower-Middle_After2015", "Lower-Middle_After2015")

est_G7 <- get_strata_estimates(model_2, "GroupPeriodLow_Before2015", "Low_Before2015")
est_G8 <- get_strata_estimates(model_2, "GroupPeriodLow_After2015", "Low_After2015")


new_data <- covariates_get(model_2)

new_data[, "GroupPeriodHigh_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_After2015"] <- 0
new_data[, "GroupPeriodLower-Middle_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_After2015"] <- 0
new_data[, "GroupPeriodLower-Middle_Before2015"] <- 0
new_data[, "GroupPeriodLower-Middle_After2015"] <- 0
new_data[, "GroupPeriodLow_Before2015"] <- 0
new_data[, "GroupPeriodLow_After2015"] <- 0
pred <- predict(model_2, new_data, label = "High_After2015")

res <- bind_rows(est_G1,pred, est_G3, est_G4,est_G5,est_G6, est_G7, est_G8) %>%
          filter(TopicID %in% c(1, 2, 3, 4, 5))
labels <- unique(res$label)

library(ggplot2)
ggplot(res, aes(x = label, ymin = Lower, ymax = Upper, group = Topic)) +
  geom_errorbar(width = 0.1) +
  coord_flip() +
  facet_wrap(~Topic) +
  geom_point(aes(x = label, y = Point)) +
  scale_x_discrete(limits = rev(labels)) +
  xlab("Income Group") +
  ylab(expression(paste("Mean of ", theta))) +
  theme_bw()


```


# TIME BIIITCH

```{r}
#topic_modelling_df
```


```{r, echo=FALSE}
# Define a function for processing one income level
prepare_keyATM_data <- function(df, income_level, bigrams, keywords) {
  topic_modelling <- df %>%
    filter(Income.Level == income_level) %>%
    mutate(doc_id = paste0("text", row_number()))

  # Tokenize
  tokenized_docs <- strsplit(topic_modelling$text, " ")
  tokens_obj <- tokens(as.list(tokenized_docs))
  tokens_obj <- tokens_compound(tokens_obj, phrase(bigrams))

  # Create and trim DFM
  dfm_obj <- dfm(tokens_obj) %>%
    dfm_trim(min_termfreq = 1, min_docfreq = 1) %>%
    dfm_subset(ntoken(.) > 0)

  # Align metadata with DFM
  docvars_time <- topic_modelling %>%
  filter(doc_id %in% docnames(dfm_obj)) %>%
  mutate(
    Year = year(ymd(paste0(Year, "-01-01")))
  ) %>%
  arrange(Year) %>%
  mutate(
    Period = match(Year, sort(unique(Year)))  # ascending index starting at 1
  )

  stopifnot(nrow(docvars_time) == ndoc(dfm_obj))
  
  docvars(dfm_obj) <- docvars_time
  
  keyATM_docs <- keyATM_read(texts = dfm_obj)
  
  model_result <- keyATM(
    docs              = keyATM_docs,
    no_keyword_topics = 1,
    keywords          = keywords,
    model             = "dynamic",
    model_settings    = list(
      time_index = docvars_time$Period,  # <-- FIXED
      num_states = 2
    ),
    options = list(seed = 123, store_theta = TRUE, thinning = 5)  # <-- typo fixed: "thinnin"
  )
  saveRDS(
    model_result,
    file = paste0(
      "C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time_",
      income_level,
      ".rds"
    )
  )

  list(
    model = model_result,
    keyATM_docs = keyATM_docs,
    docvars = docvars_time,
    dfm = dfm_obj,
    time_index = docvars_time$Period
  )
}

income_level <- c(1, 2, 3, 4)

model_outputs <- list()

for (i in income_level) {
  cat("Running model for income level", i, "\n")
  model_outputs[[paste0("income_", i)]] <- prepare_keyATM_data(topic_modelling_df, i, bigrams, keywords)
}
```


```{r}
# Access model and metadata for income group 1
model_1      <- model_outputs[["income_1"]]$model
year_labels  <- sort((model_outputs[["income_1"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_1, time_index_label = year_labels, xlab = "Year")

```

```{r}
# Access model and metadata for income group 2
model_2      <- model_outputs[["income_2"]]$model
year_labels  <- sort((model_outputs[["income_2"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_2, time_index_label = year_labels, xlab = "Year")
```


```{r}
# Access model and metadata for income group 1
model_3      <- model_outputs[["income_3"]]$model
year_labels  <- sort((model_outputs[["income_3"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_3, time_index_label = year_labels, xlab = "Year")
```

```{r}
# Access model and metadata for income group 1
model_4      <- model_outputs[["income_4"]]$model
year_labels  <- sort((model_outputs[["income_4"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_4, time_index_label = year_labels, xlab = "Year")
```


```{r}
# Define a function for processing one income level
prepare_keyATM_data <- function(df, income_level, bigrams, climate_keywords_dict) {
  topic_modelling <- df %>%
    filter(Income.Level == income_level) %>%
    mutate(doc_id = paste0("text", row_number()))

  # Tokenize
  tokenized_docs <- strsplit(topic_modelling$text, " ")
  tokens_obj <- tokens(as.list(tokenized_docs))
  tokens_obj <- tokens_compound(tokens_obj, phrase(bigrams))

  # Create and trim DFM
  dfm_obj <- dfm(tokens_obj) %>%
    dfm_trim(min_termfreq = 1, min_docfreq = 1) %>%
    dfm_subset(ntoken(.) > 0)

  # Align metadata with DFM
  docvars_time <- topic_modelling %>%
  filter(doc_id %in% docnames(dfm_obj)) %>%
  mutate(
    Year = year(ymd(paste0(Year, "-01-01")))
  ) %>%
  arrange(Year) %>%
  mutate(
    Period = match(Year, sort(unique(Year)))  # ascending index starting at 1
  )

  stopifnot(nrow(docvars_time) == ndoc(dfm_obj))
  
  docvars(dfm_obj) <- docvars_time
  
  keyATM_docs <- keyATM_read(texts = dfm_obj)
  
  model_result <- keyATM(
    docs              = keyATM_docs,
    no_keyword_topics = 1,
    keywords          = climate_keywords_dict,
    model             = "dynamic",
    model_settings    = list(
      time_index = docvars_time$Period,  # <-- FIXED
      num_states = 2
    ),
    options = list(seed = 123, store_theta = TRUE, thinning = 5)  # <-- typo fixed: "thinnin"
  )
  saveRDS(
    model_result,
    file = paste0(
      "C:/Users/Alvaro Millan Ruiz/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time_dict",
      income_level,
      ".rds"
    )
  )

  list(
    model = model_result,
    keyATM_docs = keyATM_docs,
    docvars = docvars_time,
    dfm = dfm_obj,
    time_index = docvars_time$Period
  )
}

income_level <- c(1, 2, 3, 4)

model_outputs <- list()

for (i in income_level) {
  cat("Running model for income level", i, "\n")
  model_outputs[[paste0("income_", i)]] <- prepare_keyATM_data(topic_modelling_df, i, bigrams, climate_keywords_dict)
}
```

```{r}
# Access model and metadata for income group 1
model_1      <- model_outputs[["income_1"]]$model
year_labels  <- sort((model_outputs[["income_1"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_1, time_index_label = year_labels, xlab = "Year")
```

```{r}
# Access model and metadata for income group 2
model_2      <- model_outputs[["income_2"]]$model
year_labels  <- sort((model_outputs[["income_2"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_2, time_index_label = year_labels, xlab = "Year")
```

```{r}
# Access model and metadata for income group 2
model_3      <- model_outputs[["income_3"]]$model
year_labels  <- sort((model_outputs[["income_3"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_3, time_index_label = year_labels, xlab = "Year")
```

```{r}
# Access model and metadata for income group 4
model_4      <- model_outputs[["income_4"]]$model
year_labels  <- sort((model_outputs[["income_4"]]$docvars$Year))

# Plot with year labels
plot_timetrend(model_4, time_index_label = year_labels, xlab = "Year")
```


