---
title: "KeyATM"
author: "Alvaro millan"
date: "2025-06-06"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r}

```


```{r}
install.packages("plotly")

# install.packages("quanteda")
```


```{r}
#library(text)
library(keyATM)
library(quanteda)
library(quanteda.textstats)
library(ggplot2)
library(lubridate)
library(dplyr)
```

```{r}
final_df <- read.csv("C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/Final_df.csv")
```

```{r}
# Prepare the dataframe for topic modelling
topic_modelling_df <- final_df %>%
  select(cleaned_speeches_postagging_expanded, Year, Income.Level, ISO.Code) %>%
  rename(text = cleaned_speeches_postagging_expanded)
```


# Check for bigrams MANUALLY

```{r}
bigrams <- read.csv("C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/bigrams.csv")
```

```{r}
bigrams = c("climate change", "global warming", "global warm","cap and trade", "paris accord", "emissions trading", "global average temperature", "kyoto protocol", "changing climate" ,"climate resilience","climate decay", "carbon dioxide", "carbon-dioxide","climate politics", "framework convention climate change", "bali roadmap", "bali action plan", "greenhouse gas", "greenhouse-gas","greenhouse effect", "climate mitigation", "climate action", "emissions", "temperature", "extreme weather", "global environmental change", "global environment", "global environmental" ,"climate variability", "low carbon", "renewable energy", "carbon emission", "climate pollutant", "climate pollutants", "carbon tax", "carbon footprint", "carbon neutrality", "net-zero","net zero","net-zero","climate crisis", "climate summit", "climate catastrophe", "climate justice", "climate emergency", "climate funding", "climate fund", "climate financing", "climate finance","climate peace", "climate agreement", "climate security", "climate ambition", "climate issue", "climate impact", "climate conference", "climate event", "climate challenge", "climate trust", "climate negotiation", "climate catastrophe", "climate risk", "climate goal", "climate change-related", "climate regime", "climate resilient", "climate policy", "carbon market", "carbon sink", "green climate", "green economy", "emission reduction", "emissions reduction", "carbon neutral","ozone layer", "emissions trading scheme", "co2 emission", "united nation")

tokenized_docs <- strsplit(topic_modelling_df$text, " ")

# Convert your tokenized list to a quanteda tokens object
tokens_obj <- tokens(as.list(tokenized_docs)) 


tokens_obj <- tokens_compound(tokens_obj, phrase(bigrams))

# 6. Create DFM and trim
dfm_obj <- dfm(tokens_obj) %>%
  dfm_trim(min_termfreq = 1, min_docfreq = 1)

# 7. Remove empty documents (critical for KeyATM)
dfm_obj <- dfm_subset(dfm_obj, ntoken(dfm_obj) > 0)

kept_docs <- docnames(dfm_obj)  # These are "text1", "text2", etc.

# 2. Create matching IDs in your original data
topic_modelling_df <- topic_modelling_df %>%
  mutate(doc_id = paste0("text", row_number()))  # Create matching IDs

docvars <- topic_modelling_df %>%
  filter(doc_id %in% kept_docs) %>%           # Keep only docs that exist in DFM
  arrange(match(doc_id, kept_docs)) %>%       # Put in same order as DFM
  transmute(
    Year = as.numeric(Year),
    Income.Group = factor(
      Income.Level,
      levels = c(1, 2, 3, 4),
      labels = c("Low", "Lower-Middle", "Upper-Middle", "High") # first level ("Before2015") is treated as the baseline dummy variable
    ),
    Year_std = as.vector(scale(Year))
  ) %>%
  mutate(
    Period = factor(
      ifelse(Year < 2015, "Before2015", "After2015"), 
      levels = c("Before2015", "After2015")
    )
  )

# Ensure docvars rows match dfm_obj EXACTLY
stopifnot(nrow(docvars) == ndoc(dfm_obj))

# 3. First attach docvars to the DFM (proper quanteda method)
docvars(dfm_obj) <- docvars  # Attach your prepared metadata

# 4. Convert to keyATM format (preserving docvars)
keyATM_docs <- keyATM_read(texts = dfm_obj)
```


```{r}
keywords <- list(
  Climate = c("climate_change", "global_warming", "global_warm","cap_and_trade", "paris_accord", "emissions_trading", "global_average_temperature", "kyoto_protocol", "changing_climate" ,"climate_resilience","climate_decay", "carbon_dioxide", "carbon_-_dioxide","climate_politics", "framework_convention_climate_change", "bali_roadmap", "bali_action_plan", "greenhouse_gas", "greenhouse_-_gas","greenhouse_effect", "climate_mitigation", "climate_action", "emissions", "temperature", "extreme_weather", "global_environmental_change", "global_environment", "global_environmental" ,"climate_variability", "low_carbon", "renewable_energy", "carbon_emission", "climate_pollutant", "climate_pollutants", "carbon_tax", "carbon_footprint", "carbon_neutrality", "net_-_zero","net_zero","net_-_zero","climate_crisis", "climate_summit", "climate_catastrophe", "climate_justice", "climate_emergency", "climate_funding", "climate_fund", "climate_financing", "climate_finance","climate_peace", "climate_agreement", "climate_security", "climate_ambition", "climate_issue", "climate_impact", "climate_conference", "climate_event", "climate_challenge", "climate_trust", "climate_negotiation", "climate_catastrophe", "climate_risk", "climate_goal", "climate_change_-_related", "climate_regime", "climate_resilient", "climate_policy", "carbon_market", "carbon_sink", "green_climate", "green_economy", "emission_reduction", "emissions_reduction", "carbon_neutral","ozone_layer", "emissions_trading_scheme", "co2_emission", "ghg", "ghge", "co2", "ipcc","decarbonisation", "decarbonization")
)
```

```{r}
climate_keywords_dict <- list(
  
  # 1. Climate Science & Impacts
  science_impacts = c(
    "climate_change", "global_warm", "global_warming", "global_average_temperature",
        "climate_variability", "extreme_weather", "climate_impact",
        "greenhouse_effect", "temperature", "climate_catastrophe",
        "climate_risk", "ozone_layer", "global_environmental_change",
        "global_environmental", "global_environment", 
        "climate_change-related", "climate_risk", "changing_climate",
        "climate_decay"
  ),
  
  # 2. Policy & Agreements
  policy_agreements = c(
    "paris_accord", "kyoto_protocol", "unfccc", "climate_policy",
        "framework_convention_on_climate_change", "framework_convention_climate_change",
        "climate_agreement", "climate_regime", "climate_negotiation", "climate_ambition",
        "climate_security", "bali_roadmap", "ipcc", "bali_action_plan"
  ),
  
  # 3. Carbon & Emissions
  carbon_emissions = c(
    "carbon_dioxide", "co2", "carbon_emission", "carbon_tax",
        "carbon_footprint", "carbon_neutrality", "carbon_neutral",
        "carbon_market", "carbon_sink", "low_carbon", "emissions",
        "emission_reduction", "emissions_reduction", "ghg", "ghge",
        "climate_pollutant", "climate_pollutants", "carbon_neutral",
        "greenhouse_gas", "decarbonisation", "decarbonization", 
        "greenhouse_-_gas"
  ),
  
  # 4. Climate Action & Solutions
  action_solutions = c(
     "climate_action", "climate_mitigation", "renewable_energy",
        "climate_resilience", "climate_resilient", "green_economy",
        "climate_funding", "climate_fund", "climate_financing", "climate_finance",
        "net-zero", "net_zero", "green_climate", "cap_and_trade",
        "emissions_trading_scheme", "emissions_trading"
  ),
  
  # 5. Sociopolitical Climate Issues
  sociopolitical = c(
    "climate_justice", "climate_emergency", "climate_crisis",
        "climate_summit", "climate_politics", "climate_peace",
        "climate_challenge", "climate_goal", "climate_issue",
        "climate_event", "climate_conference", "climate_trust"
  )
)

```


```{r}
# 4. Now run keyATM with covariates
#model_dict <- keyATM(
#  docs = keyATM_docs,
#  keywords = climate_keywords_dict,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
#    covariates_formula = ~ Income.Group + Period,
#    covariates_data = docvars(dfm_obj),  # Pull from attached docvars
#    standardize = "none"
#  ), 
#   options = list(seed = 123)
#)

#saveRDS(model_dict, file = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_dict.rds")
```


```{r}
# 4. Now run keyATM with covariates
#model <- keyATM(
#  docs = keyATM_docs,
#  keywords = keywords,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
    #covariates_formula = ~ Income.Group * Year_std,
#    covariates_formula = ~ Income.Group + Period,
#    covariates_data = docvars(dfm_obj),  # Pull from attached docvars
#    standardize = "none"
#  ), 
#   options = list(seed = 123)
#)

#saveRDS(model, file = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model.rds")
```


```{r}
# Choose whicever u want to test for, the one that is suborganized into different topics, keyATM_model_dict.rds, or the ones that is simple keyATM_model.rds

model <- readRDS("C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model.rds")

model_dict <- readRDS("C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_dict.rds")
```





2
** The by_strata_DocTopic() function can display the marginal posterior means of document-topic distributions for each value of (discrete) covariates. **  

```{r}
strata_topic <- by_strata_DocTopic(
  model, by_var = "PeriodAfter2015",
  labels = c("1990_2014", "2015_24")
)

strata_topic_dict <- by_strata_DocTopic(
  model_dict, by_var = "PeriodAfter2015",
  labels = c("1990_2014", "2015_24")
)
```


** The figure shows the marginal posterior means of document-topic distributions and the 90% credible intervals of them for each value of covariates. ** 


```{r}
library(ggplotify)

fig_doctopic <- plot(strata_topic, var_name = "Period", show_topic = c(1))
fig_doctopic
png(
  filename = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS/CI.Before_After_Paris_Agreement.png",
  width = 10,
  height = 6,
  units = "in",     # specify units for width and height
  res = 300         # resolution
)

# Generate the plot inside the device
plot(strata_topic, var_name = "Period", show_topic = c(1))



```


```{r}
fig_doctopic <- plot(strata_topic_dict, var_name = "Period", show_topic = c(1,2,3,4,5))

png(
  filename = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS/CI.Before_After_Paris_Agreement_by_subtopic",
  width = 10,
  height = 6,
  units = "in",     # specify units for width and height
  res = 300         # resolution
)

# Generate the plot inside the device
plot(strata_topic_dict, var_name = "Period", show_topic = c(1,2,3,4,5))

# Close the device to save the file
dev.off()
```


** We can visualize results by covariate with by = "covariate" argument. The plot below combines two panels in the previous plot and display in the same panel. ** 


```{r}
# run only if you have selected the keyATM_model_dict.rds
key_viz <- visualize_keywords(
  docs = keyATM_docs,
  keywords = climate_keywords_dict,
  prune = TRUE, # or even Inf to show everything
  label_size = 2.5
)

viz_data_filtered <- values_fig(key_viz)


climate_keyword_plot <- viz_data_filtered %>%
  filter(`Proportion(%)` > 0) %>%
  ggplot(aes(x = reorder(Word, `Proportion(%)`), y = `Proportion(%)`, fill = Topic)) +
  geom_col() +
  coord_flip() +
  labs(x = "Keyword", y = "Proportion (%)", fill = "Topic Group") +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA)
  )


climate_keyword_plot

ggsave(
  filename = "keyword_proportion_by_subtopic.PNG",
  plot = climate_keyword_plot,
  path = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS",
  width = 10,       # adjust width (in inches)
  height = 6,       # adjust height (in inches)
  dpi = 300         # high-resolution for print
)
```

** Using the output of the keyATM, we can calculate 90% credible intervals of the differences in the mean of document-topic distribution. **

** Since we set the years prior to 2015 dummy as the baseline when constructing factor for this variable, the comparison is the relative increase or decrease from the years prior to 2015 to the years from 2015 to 2024. 

```{r}
theta1 <- strata_topic$theta[[1]]  # Topic proportions for 1990–2014
theta2 <- strata_topic$theta[[2]]  # Topic proportions for 2015–2024
theta_diff <- theta2[, c(1)] - theta1[, c(1)]
theta_diff_quantile <- quantile(theta_diff, c(0.025, 0.5, 0.975)) # Difference in topic 1
# By how much did the average prevalence of topic 1 (Climate) change between 1990–2014 and 2015–2024? 
theta_diff_quantile
```
```{r}
# Assuming theta1 is your dataframe:
skewness_val <- moments::skewness(theta2[, 1])  # Use Column 1 (Topic 1 proportions)
skewness_val
```




```{r}
theta1 <- strata_topic_dict$theta[[1]]  # Topic proportions for 1990–2014
theta2 <- strata_topic_dict$theta[[2]]  # Topic proportions for 2015–2024
theta_diff <- theta2[, c(1,2,3,4,5)] - theta1[, c(1,2,3,4,5)]  # focus on two topics
theta_diff_quantile <- apply(theta_diff, 2, quantile, probs = c(0.025, 0.5, 0.975)) # prevalence Lower bound of the 95% credible interval. Median of the difference (i.e. central estimate). Upper bound of the 95% credible interval.
theta_diff_quantile
```


* This topic became significantly more prevalent after 2015 — with high certainty. * 

*Furthermore, we can use the predict() function to get the predicted mean of the document-topic distribution for three party categories.*


```{r}
get_strata_estimates <- function(model, var, label) {
  strata <- by_strata_DocTopic(model, by_var = var, labels = c(paste0("Non-", label), label))
  summary(strata)[[label]]
}

est_high      <- get_strata_estimates(model, "Income.GroupHigh", "High")
est_upp_mid   <- get_strata_estimates(model, "Income.GroupUpper-Middle", "Upper-Middle")
est_low_mid   <- get_strata_estimates(model, "Income.GroupLower-Middle", "Lower-Middle")


new_data <- covariates_get(model)

new_data[, "Income.GroupHigh"] <- 0
new_data[, "Income.GroupUpper-Middle"] <- 0
new_data[, "Income.GroupLower-Middle"] <- 0
pred <- predict(model, new_data, label = "Low")

res <- bind_rows(est_high, est_upp_mid, est_low_mid, pred) %>%
          filter(TopicID %in% 1)

#res <- bind_rows(est_high, est_upp_mid, est_low_mid, pred) %>%
          #filter(TopicID %in% c(1, 2, 3, 4, 5))
labels <- unique(res$label)

# The mean topic prevalence (theta) for Topic 1 across income groups. 
# Error bars show 90% credible intervals.

ggplot(res, aes(x = label, ymin = Lower, ymax = Upper, group = Topic)) +
  geom_errorbar(width = 0.1) +
  coord_flip() +
  facet_wrap(~Topic) +
  geom_point(aes(x = label, y = Point)) +
  scale_x_discrete(limits = rev(labels)) +
  xlab("Income Group") +
  ylab(expression(paste("Mean of ", theta))) +
  theme_bw()

# θ (theta) represents the mean document-topic distribution — specifically, the average proportion of a document that is about Topic 1 ("Climate") for each income group
```
* The average prevalence (θ) of this topic in UN speeches, broken down by income group. *

* All income groups discuss "Climate" relatively equally. * 
* Low income group they discuss it in average way less * 

*WHAT ABOUT ADDING A TIME THING 2015 ONWARDS* 


```{r }
docvars_2 <- topic_modelling_df %>%
  filter(doc_id %in% kept_docs) %>%
  arrange(match(doc_id, kept_docs)) %>%
  transmute(
    Year = as.numeric(Year),
    Income.Group = factor(
      Income.Level,
      levels = c(1, 2, 3, 4),
      labels = c("Low", "Lower-Middle", "Upper-Middle", "High")
    ),
    Period = factor(
      ifelse(Year < 2015, "Before2015", "After2015"),
      levels = c("Before2015", "After2015")
    ),
    GroupPeriod = paste0(Income.Group, "_", Period),
    Year_std = as.vector(scale(Year))
)

# Attach docvars to DFM
stopifnot(nrow(docvars_2) == ndoc(dfm_obj))
docvars(dfm_obj) <- docvars_2

# Convert to keyATM format
keyATM_docs <- keyATM_read(texts = dfm_obj)

# Fit the keyATM model
#model_dict_2 <- keyATM(
#  docs = keyATM_docs,
#  keywords = climate_keywords_dict,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
#    covariates_formula = ~ GroupPeriod,
#    covariates_data = docvars(dfm_obj),
#    standardize = "none"
#  ),
#  options = list(seed = 123)
#  )
# Save model
#saveRDS(model_dict_2, file = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time2015_dict.rds")

#model_2 <- keyATM(
#  docs = keyATM_docs,
#  keywords = keywords,
#  no_keyword_topics = 1,
#  model = "covariates",
#  model_settings = list(
#    covariates_formula = ~ GroupPeriod,
#    covariates_data = docvars(dfm_obj),
#    standardize = "none"
#  ),
#  options = list(seed = 123)
#  )

#saveRDS(model_2, file = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time2015.rds")

```

```{r}
model_2_dict <- readRDS("C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time2015_dict.rds")

est_G1 <- get_strata_estimates(model_2_dict, "GroupPeriodHigh_Before2015", "High_Before2015")

est_G3 <- get_strata_estimates(model_2_dict, "GroupPeriodUpper-Middle_Before2015", "Upper-Middle_Before2015")
est_G4 <- get_strata_estimates(model_2_dict, "GroupPeriodUpper-Middle_After2015", "Upper-Middle_After2015")

est_G5 <- get_strata_estimates(model_2_dict, "GroupPeriodLower-Middle_Before2015", "Lower-Middle_Before2015")
est_G6 <- get_strata_estimates(model_2_dict, "GroupPeriodLower-Middle_After2015", "Lower-Middle_After2015")

est_G7 <- get_strata_estimates(model_2_dict, "GroupPeriodLow_Before2015", "Low_Before2015")
est_G8 <- get_strata_estimates(model_2_dict, "GroupPeriodLow_After2015", "Low_After2015")


new_data <- covariates_get(model_2_dict)

new_data[, "GroupPeriodHigh_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_After2015"] <- 0
new_data[, "GroupPeriodLower-Middle_Before2015"] <- 0
new_data[, "GroupPeriodLower-Middle_After2015"] <- 0
new_data[, "GroupPeriodLow_Before2015"] <- 0
new_data[, "GroupPeriodLow_After2015"] <- 0
pred <- predict(model_2_dict, new_data, label = "High_After2015")

res <- bind_rows(est_G1,pred, est_G3, est_G4,est_G5,est_G6, est_G7, est_G8) %>%
          filter(TopicID %in% c(1, 2, 3, 4, 5))

label_map <- c(
  "High_Before2015" = "High (1990–2014)",
  "High_After2015" = "High (2015–24)",
  "Upper-Middle_Before2015" = "Upper-Middle (1990–2014)",
  "Upper-Middle_After2015" = "Upper-Middle (2015–24)",
  "Lower-Middle_Before2015" = "Lower-Middle (1990–2014)",
  "Lower-Middle_After2015" = "Lower-Middle (2015–24)",
  "Low_Before2015" = "Low (1990–2014)",
  "Low_After2015" = "Low (2015–24)"
)

res$label <- label_map[res$label]

labels <- unique(res$label)

plot_1 <- ggplot(res, aes(x = label, ymin = Lower, ymax = Upper, group = Topic)) +
  geom_errorbar(width = 0.1) +
  coord_flip() +
  facet_wrap(~Topic) +
  geom_point(aes(x = label, y = Point)) +
  scale_x_discrete(limits = rev(labels)) +
  xlab("Income Group") +
  ylab(expression(paste("Mean of ", theta))) +
  theme_bw()

plot_1

ggsave(
  filename = "Topics change from 1990-2014 to 2015-2024 for different country incomes PLOTS.PNG",
  plot = plot_1,
  path = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS",
  width = 10,       # adjust width (in inches)
  height = 6,       # adjust height (in inches)
  dpi = 300         # high-resolution for print
)

```

```{r}
library(dplyr)

compute_diff_with_ci <- function(res_df, group_label) {
  before_label <- paste0(group_label, " (1990–2014)")
  after_label  <- paste0(group_label, " (2015–24)")

  before <- res_df %>% filter(label == before_label) %>%
    select(Topic, Point_before = Point, Lower_before = Lower, Upper_before = Upper) %>%
    mutate(SE_before = (Upper_before - Lower_before) / (2 * 1.96))
  
  after <- res_df %>% filter(label == after_label) %>%
    select(Topic, Point_after = Point, Lower_after = Lower, Upper_after = Upper) %>%
    mutate(SE_after = (Upper_after - Lower_after) / (2 * 1.96))

  diff_tbl <- inner_join(after, before, by = "Topic") %>%
    mutate(
      diff_mean = Point_after - Point_before,
      SE_diff = sqrt(SE_before^2 + SE_after^2),  # assuming independence
      diff_lower = diff_mean - 1.96 * SE_diff,
      diff_upper = diff_mean + 1.96 * SE_diff,
      Income_Group = group_label
    ) %>%
    select(Income_Group, Topic, diff_mean, diff_lower, diff_upper)
  
  return(diff_tbl)
}

# Apply function to all income groups
income_groups <- c("High", "Upper-Middle", "Lower-Middle", "Low")
final_diff_table <- bind_rows(lapply(income_groups, function(g) compute_diff_with_ci(res, g)))

# Print nicely
print(final_diff_table)

```


```{r}
model_2 <- readRDS("C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time2015.rds")

est_G1 <- get_strata_estimates(model_2, "GroupPeriodHigh_Before2015", "High_Before2015")

est_G3 <- get_strata_estimates(model_2, "GroupPeriodUpper-Middle_Before2015", "Upper-Middle_Before2015")
est_G4 <- get_strata_estimates(model_2, "GroupPeriodUpper-Middle_After2015", "Upper-Middle_After2015")

est_G5 <- get_strata_estimates(model_2, "GroupPeriodLower-Middle_Before2015", "Lower-Middle_Before2015")
est_G6 <- get_strata_estimates(model_2, "GroupPeriodLower-Middle_After2015", "Lower-Middle_After2015")

est_G7 <- get_strata_estimates(model_2, "GroupPeriodLow_Before2015", "Low_Before2015")
est_G8 <- get_strata_estimates(model_2, "GroupPeriodLow_After2015", "Low_After2015")


new_data <- covariates_get(model_2)

new_data[, "GroupPeriodHigh_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_Before2015"] <- 0
new_data[, "GroupPeriodUpper-Middle_After2015"] <- 0
new_data[, "GroupPeriodLower-Middle_Before2015"] <- 0
new_data[, "GroupPeriodLower-Middle_After2015"] <- 0
new_data[, "GroupPeriodLow_Before2015"] <- 0
new_data[, "GroupPeriodLow_After2015"] <- 0
pred <- predict(model_2, new_data, label = "High_After2015")

res <- bind_rows(est_G1,pred, est_G3, est_G4,est_G5,est_G6, est_G7, est_G8) %>%
          filter(TopicID %in% c(1))

label_map <- c(
  "High_Before2015" = "High (1990–2014)",
  "High_After2015" = "High (2015–24)",
  "Upper-Middle_Before2015" = "Upper-Middle (1990–2014)",
  "Upper-Middle_After2015" = "Upper-Middle (2015–24)",
  "Lower-Middle_Before2015" = "Lower-Middle (1990–2014)",
  "Lower-Middle_After2015" = "Lower-Middle (2015–24)",
  "Low_Before2015" = "Low (1990–2014)",
  "Low_After2015" = "Low (2015–24)"
)

res$label <- label_map[res$label]

labels <- unique(res$label)

plot_1 <- ggplot(res, aes(x = label, ymin = Lower, ymax = Upper, group = Topic)) +
  geom_errorbar(width = 0.1) +
  coord_flip() +
  facet_wrap(~Topic) +
  geom_point(aes(x = label, y = Point)) +
  scale_x_discrete(limits = rev(labels)) +
  xlab("Income Group") +
  ylab(expression(paste("Mean of ", theta))) +
  theme_bw()
plot_1

ggsave(
  filename = "Topic change from 1990-2014 to 2015-2024 for different country incomes PLOTS.PNG",
  plot = plot_1,
  path = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS",
  width = 10,       # adjust width (in inches)
  height = 6,       # adjust height (in inches)
  dpi = 300         # high-resolution for print
)

```

```{r}
# Apply function to all income groups
income_groups <- c("High", "Upper-Middle", "Lower-Middle", "Low")
final_diff_table_1 <- bind_rows(lapply(income_groups, function(g) compute_diff_with_ci(res, g)))

# Print nicely
print(final_diff_table_1)
```


# TIME BIIITCH

```{r}
#topic_modelling_df
```


```{r, echo=FALSE}
# Define a function for processing one income level
prepare_keyATM_data <- function(df, income_level, bigrams, keywords) {
  topic_modelling <- df %>%
    filter(Income.Level == income_level) %>%
    mutate(doc_id = paste0("text", row_number()))

  # Tokenize
  tokenized_docs <- strsplit(topic_modelling$text, " ")
  tokens_obj <- tokens(as.list(tokenized_docs))
  tokens_obj <- tokens_compound(tokens_obj, phrase(bigrams))

  # Create and trim DFM
  dfm_obj <- dfm(tokens_obj) %>%
    dfm_trim(min_termfreq = 1, min_docfreq = 1) %>%
    dfm_subset(ntoken(.) > 0)

  # Align metadata with DFM
  docvars_time <- topic_modelling %>%
  filter(doc_id %in% docnames(dfm_obj)) %>%
  mutate(
    Year = year(ymd(paste0(Year, "-01-01")))
  ) %>%
  arrange(Year) %>%
  mutate(
    Period = match(Year, sort(unique(Year)))  # ascending index starting at 1
  )

  stopifnot(nrow(docvars_time) == ndoc(dfm_obj))
  
  docvars(dfm_obj) <- docvars_time
  
  keyATM_docs <- keyATM_read(texts = dfm_obj)
  
  model_result <- keyATM(
    docs              = keyATM_docs,
    no_keyword_topics = 1,
    keywords          = keywords,
    model             = "dynamic",
    model_settings    = list(
      time_index = docvars_time$Period,  # <-- FIXED
      num_states = 2
    ),
    options = list(seed = 123, store_theta = TRUE, thinning = 5)  # <-- typo fixed: "thinnin"
  )
  saveRDS(
    model_result,
    file = paste0(
      "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time_",
      income_level,
      ".rds"
    )
  )

  list(
    model = model_result,
    keyATM_docs = keyATM_docs,
    docvars = docvars_time,
    dfm = dfm_obj,
    time_index = docvars_time$Period
  )
}

income_level <- c(1, 2, 3, 4)

model_outputs <- list()

for (i in income_level) {
  cat("Running model for income level", i, "\n")
  model_outputs[[paste0("income_", i)]] <- prepare_keyATM_data(topic_modelling_df, i, bigrams, keywords)
}
```


```{r}
library(dplyr)
library(ggplot2)
library(purrr)
library(keyATM)  # if not already loaded

for (i in 1:4) {
  income_key <- paste0("income_", i)
  
  cat("Creating keyword plot for", income_key, "\n")
  
  keyATM_docs <- model_outputs[[income_key]]$keyATM_docs
  
  # Step 1: Create keyword visualization object
  key_viz <- visualize_keywords(
    docs = keyATM_docs,
    keywords = climate_keywords_dict,  # replace with your actual keyword dict variable
    prune = TRUE,
    label_size = 2.5
  )
  
  # Step 2: Extract proportions
  viz_data_filtered <- values_fig(key_viz)
  
  # Step 3: Filter and plot
  climate_keyword_plot <- viz_data_filtered %>%
    filter(`Proportion(%)` > 0) %>%
    ggplot(aes(x = reorder(Word, `Proportion(%)`), y = `Proportion(%)`, fill = Topic)) +
    geom_col() +
    coord_flip() +
    labs(
      x = "Keyword",
      y = "Proportion (%)",
      fill = "Topic Group",
      title = paste("Keyword Proportions for Income Group", i)
    ) +
    theme_minimal() +
    theme(
      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA)
    )
  
  # Step 4: Save the plot
  ggsave(
    filename = paste0("keyword_proportion_income_", i, ".png"),
    plot = climate_keyword_plot,
    path = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS",
    width = 10,
    height = 6,
    dpi = 300
  )
}

```


```{r}
calc_eti <- function(vec, ci = 0.95, point = "mean") {
  if (point == "mean") {
    point_est <- mean(vec)
  } else {
    point_est <- median(vec)
  }
  
  probs <- c((1 - ci)/2, (1 + ci)/2)
  qua <- stats::quantile(vec, probs = c((1 - ci)/2, (1 + 
            ci)/2))
  
  return(list(Lower = qua[1], Point = point_est, Upper = qua[2]))
}
```

```{r}
process_income_group <- function(income_level) {
  model <- model_outputs[[paste0("income_", income_level)]]$model
  theta <- model$theta[, 1]
  docvars_df <- model_outputs[[paste0("income_", income_level)]]$docvars
  
  data.frame(
    Country = docvars_df$ISO.Code,  # <-- Must be present in your metadata
    Year = docvars_df$Year,
    Income_Group = factor(paste("Income", income_level)),
    Theta = theta
  )
}

all_income_data <- map_dfr(1:4, process_income_group)
```


```{r}
library(tidyr)
## 3. Calculate ETI for each group-year combination
summary_stats_old <- all_income_data %>%
  group_by(Income_Group, Year) %>%
  summarise(
    ci = list(calc_eti(Theta, ci = 0.95, point = "mean")),
    .groups = "drop"
  ) %>%
  unnest_wider(ci) %>%
  rename(mean_theta = Point, ci_lower = Lower, ci_upper = Upper)

# 4. Calculate weights based on proportion of countries in each income group per year
country_weights <- all_income_data %>%
  group_by(Year, Income_Group) %>%
  summarise(n_countries = n(), .groups = "drop_last") %>%
  mutate(weight = n_countries / sum(n_countries)) %>%
  ungroup()

adjusted_data <- summary_stats_old %>%
  left_join(country_weights, by = c("Year", "Income_Group")) 

# Calculate adjusted theta (scaled by income group's proportion of countries)
final_adjusted_data <- adjusted_data %>%
  mutate(
    adjusted_theta = mean_theta * weight,
    adjusted_lower = ci_lower * weight,
    adjusted_upper = ci_upper * weight
  )


weighted_plot <- ggplot(final_adjusted_data, 
                       aes(x = Year, y = adjusted_theta, 
                      color = Income_Group, fill = Income_Group)) +
  geom_line(size = 0.8) +
  geom_ribbon(aes(ymin = adjusted_lower, ymax = adjusted_upper), 
              alpha = 0.2, color = NA) +
  geom_point(size = 1.5) +
  # Styling (preserving your preferred theme)
  labs(
    title = "Climate Prevalence Across Income Groups",
    subtitle = "Mean θ ± 95% ETI | Group's proportion of countries by Income group",
    y = expression(paste("Mean topic prevalence (", theta, ")")),
    color = "Income Group",
    fill = "Income Group",
    size = "Group size weight"
  ) +
  theme_bw() +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      panel.grid.minor = element_blank()
    ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1")

## 3. Calculate ETI for each group-year combination
summary_stats <- all_income_data %>%
  group_by(Income_Group, Year) %>%
  summarise(
    ci = list(calc_eti(Theta, ci = 0.95, point = "mean")),
    .groups = "drop"
  ) %>%
  unnest_wider(ci) %>%
  rename(mean_theta = Point, ci_lower = Lower, ci_upper = Upper)

## 4. Create the combined plot
combined_plot <- ggplot(summary_stats, aes(x = Year, y = mean_theta, 
                                        color = Income_Group, fill = Income_Group)) +
  geom_line(size = 0.8) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), 
              alpha = 0.2, color = NA) +
  geom_point(size = 1.5) +
  labs(
    title = "Climate Prevalence Across Income Groups",
    subtitle = "Mean ± 95% ETI",
    y = expression(paste("Mean of ", theta)),
    color = "Income Group",
    fill = "Income Group"
  ) +
  theme_bw() +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      panel.grid.minor = element_blank()
    ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1")

## Display the plots
combined_plot  # Single plot with all groups
# or
weighted_plot

## Save high-quality output
ggsave("income_group_comparison_combined.png", combined_plot, width = 10, height = 6, dpi = 300)
ggsave("income_group_comparison_combined_weighted.png", weighted_plot, width = 10, height = 6, dpi = 300)
```


```{r}
# Define a function for processing one income level
prepare_keyATM_data <- function(df, income_level, bigrams, climate_keywords_dict) {
  topic_modelling <- df %>%
    filter(Income.Level == income_level) %>%
    mutate(doc_id = paste0("text", row_number()))

  # Tokenize
  tokenized_docs <- strsplit(topic_modelling$text, " ")
  tokens_obj <- tokens(as.list(tokenized_docs))
  tokens_obj <- tokens_compound(tokens_obj, phrase(bigrams))

  # Create and trim DFM
  dfm_obj <- dfm(tokens_obj) %>%
    dfm_trim(min_termfreq = 1, min_docfreq = 1) %>%
    dfm_subset(ntoken(.) > 0)

  # Align metadata with DFM
  docvars_time <- topic_modelling %>%
  filter(doc_id %in% docnames(dfm_obj)) %>%
  mutate(
    Year = year(ymd(paste0(Year, "-01-01")))
  ) %>%
  arrange(Year) %>%
  mutate(
    Period = match(Year, sort(unique(Year)))  # ascending index starting at 1
  )

  stopifnot(nrow(docvars_time) == ndoc(dfm_obj))
  
  docvars(dfm_obj) <- docvars_time
  
  keyATM_docs <- keyATM_read(texts = dfm_obj)
  
  model_result <- keyATM(
    docs              = keyATM_docs,
    no_keyword_topics = 1,
    keywords          = climate_keywords_dict,
    model             = "dynamic",
    model_settings    = list(
      time_index = docvars_time$Period,  # <-- FIXED
      num_states = 2
    ),
    options = list(seed = 123, store_theta = TRUE, thinning = 5)  # <-- typo fixed: "thinnin"
  )
  saveRDS(
    model_result,
    file = paste0(
      "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/keyATM_model_time_dict",
      income_level,
      ".rds"
    )
  )

  list(
    model = model_result,
    keyATM_docs = keyATM_docs,
    docvars = docvars_time,
    dfm = dfm_obj,
    time_index = docvars_time$Period
  )
}

income_level <- c(1, 2, 3, 4)

model_outputs_dict <- list()

for (i in income_level) {
  cat("Running model for income level", i, "\n")
  model_outputs_dict[[paste0("income_", i)]] <- prepare_keyATM_data(topic_modelling_df, i, bigrams, climate_keywords_dict)
}
```


```{r}
for (i in 1:4) {
  income_key <- paste0("income_", i)
  
  cat("Creating keyword plot for", income_key, "\n")
  
  keyATM_docs <- model_outputs_dict[[income_key]]$keyATM_docs
  
  # Step 1: Create keyword visualization object
  key_viz <- visualize_keywords(
    docs = keyATM_docs,
    keywords = climate_keywords_dict,  # replace with your actual keyword dict variable
    prune = TRUE,
    label_size = 2.5
  )
  
  # Step 2: Extract proportions
  viz_data_filtered <- values_fig(key_viz)
  
  # Step 3: Filter and plot
  climate_keyword_plot <- viz_data_filtered %>%
    filter(`Proportion(%)` > 0) %>%
    ggplot(aes(x = reorder(Word, `Proportion(%)`), y = `Proportion(%)`, fill = Topic)) +
    geom_col() +
    coord_flip() +
    labs(
      x = "Keyword",
      y = "Proportion (%)",
      fill = "Topic Group",
      title = paste("Keyword Proportions for Income Group", i)
    ) +
    theme_minimal() +
    theme(
      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA)
    )
  
  # Step 4: Save the plot
  ggsave(
    filename = paste0("keyword_proportion_income_", i, "dict_model.png"),
    plot = climate_keyword_plot,
    path = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS",
    width = 10,
    height = 6,
    dpi = 300
  )
}
```



```{r}
library(ggplot2)
library(dplyr)
library(purrr)

# 1. Data preparation function
prepare_topic_data <- function(topic_number) {
  map_dfr(1:4, ~{
    model <- model_outputs_dict[[paste0("income_", .x)]]$model
    data.frame(
      Year = model_outputs_dict[[paste0("income_", .x)]]$docvars$Year,
      Theta = model$theta[, topic_number],
      Income_Group = factor(paste("Income", .x), 
      levels = paste("Income", 1:4))
    )
  }) %>% 
    group_by(Income_Group, Year) %>% 
    summarise(
      mean_theta = mean(Theta),
      ci_lower = quantile(Theta, 0.025),
      ci_upper = quantile(Theta, 0.975),
      .groups = "drop"
    )
}

# 2. Create consistent plotting function
create_topic_plot <- function(data, topic_name) {
  ggplot(data, aes(x = Year, y = mean_theta, 
                  color = Income_Group, fill = Income_Group)) +
    geom_line(linewidth = 0.8) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), 
                alpha = 0.2, color = NA) +
    geom_point(size = 2.5) +
    scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.05))) +
    scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3")) +
    scale_fill_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3")) +
    labs(
      title = paste(topic_name, "Prevalence Across Income Groups"),
      subtitle = "Mean ± 95% ETI",
      y = expression(paste("Mean of ", theta)),
      x = "Year"
    ) +
    theme_bw() +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      panel.grid.minor = element_blank()
    )
}

# 3. Create and save all plots
topic_names <- c("Science Impacts", "Policy Agreements", 
                 "Carbon Emissions", "Climate Actions & Solutions", 
                 "Sociopolitical Climate Issues")

walk(1:5, ~{
  topic_data <- prepare_topic_data(.x)
  p <- create_topic_plot(topic_data, topic_names[.x])
  
  # Save each plot
  ggsave(paste0("topic_", .x, "_prevalence.png"), p, 
         width = 8, height = 6, dpi = 300)
  
  # Print to screen
  print(p)
})

# 4. Combine all plots into one multi-panel figure (alternative)
all_plots <- map(1:5, ~{
  create_topic_plot(prepare_topic_data(.x), topic_names[.x]) + 
    theme(legend.position = "none")
})

```


```{r}
library(ggplot2)
library(dplyr)
library(purrr)
library(dplyr)

prepare_topic_data <- function(topic_number) {
  map_dfr(1:4, ~{
    model <- model_outputs_dict[[paste0("income_", .x)]]$model
    docvars <- model_outputs_dict[[paste0("income_", .x)]]$docvars
    
    # Create dataframe with all required columns
    data.frame(
      Year = docvars$Year,
      ISO_Code = docvars$ISO.Code,  # Using the confirmed column name
      Theta = model$theta[, topic_number],
      Income_Group = factor(paste("Income", .x), levels = paste("Income", 1:4)),
      stringsAsFactors = FALSE
    )
  }) 
}

# Get all topics data with ISO codes
all_topics_data <- map_dfr(1:5, ~{
  prepare_topic_data(.x) %>% 
    mutate(Topic = paste("Topic", .x))
})

# 1. Calculate weights PER TOPIC
topic_country_weights <- all_topics_data %>%
  group_by(Topic) %>%  # First group by topic
  distinct(Year, Income_Group, ISO_Code) %>%
  count(Year, Income_Group, name = "n_countries") %>%
  group_by(Topic, Year) %>%  # Then group by topic AND year
  mutate(prop = n_countries / sum(n_countries)) %>%
  ungroup()

## 3. Calculate ETI for each group-year-topic combination
summary_stats_old_topic <- all_topics_data %>%
  group_by(Income_Group, Year, Topic) %>%
  summarise(
    ci = list(calc_eti(Theta, ci = 0.95, point = "mean")),
    .groups = "drop"
  ) %>%
  unnest_wider(ci) %>%
  rename(mean_theta = Point, ci_lower = Lower, ci_upper = Upper)

adjusted_data_dict <- summary_stats_old_topic %>%
  left_join(topic_country_weights, by = c("Topic", "Year", "Income_Group"))

final_adjusted_data <- summary_stats_old_topic %>%
  left_join(topic_country_weights, by = c("Topic", "Year", "Income_Group")) %>%
  rename(weight = prop) %>%  # First rename weight to prop
  mutate(
    # Then use prop for calculations (NOT weight, which no longer exists after rename)
    adjusted_theta = mean_theta * weight,
    adjusted_lower = ci_lower * weight,
    adjusted_upper = ci_upper * weight
  )


create_weighted_plot <- function(data, topic_name) {
  ggplot(data, aes(x = Year, y = adjusted_theta, 
                  color = Income_Group, fill = Income_Group)) +
    geom_line(linewidth = 0.8) +
    geom_ribbon(aes(ymin = adjusted_lower, ymax = adjusted_upper), 
                alpha = 0.2, color = NA) +
    geom_point(size = 2.5) +
    scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.05))) +
    scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3")) +
    scale_fill_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3")) +
    #scale_size_continuous(
    #  range = c(2, 6),
    #  breaks = c(min(data$n_countries), 
    #            median(data$n_countries), 
    #            max(data$n_countries)),
    #  name = "Number of countries"
    # ) +
    labs(
      title = paste(topic_name, "Prevalence (Weighted)"),
      subtitle = "Adjusted Mean θ ± 95% ETI | Group's proportion of countries by Income group",
      y = expression(paste("Weighted Mean ", theta)),
      x = "Year"
    ) +
    theme_bw() +
    theme(
      legend.position = "bottom",
      legend.box = "horizontal",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      panel.grid.minor = element_blank(),
      legend.spacing.x = unit(0.2, "cm")
    )
}

# 3. Create and save all plots
topic_names <- c("Science Impacts", "Policy Agreements", 
                 "Carbon Emissions", "Climate Actions & Solutions", 
                 "Sociopolitical Climate Issues")

# Loop to create and save weighted topic plots
walk(1:5, ~{
  topic_index <- .x
  topic_label <- paste("Topic", topic_index)
  
  # Filter data for this topic
  topic_data <- final_adjusted_data %>% 
    filter(Topic == topic_label)
  
  # Create the plot using the correct function name
  p <- create_weighted_plot(topic_data, topic_names[topic_index])
  
  # Save each plot (ggsave was missing)
  ggsave(
    filename = paste0("topic_", topic_index, "_prevalence_WEIGHTED.png"),
    plot = p,
    path = "C:/Users/alvar/OneDrive/Escritorio/BDS/Block_5/NLP/Project/NLP_BDS",
    width = 8,
    height = 6,
    dpi = 300
  )
  
  # Print to screen
  print(p)
})

```

```{r}
# 1. Data preparation (keep raw Theta values)
prepare_topic_data <- function(topic_number) {
  map_dfr(1:4, ~{
    model <- model_outputs_dict[[paste0("income_", .x)]]$model
    docvars <- model_outputs_dict[[paste0("income_", .x)]]$docvars
    
    data.frame(
      Year = docvars$Year,
      ISO_Code = docvars$ISO.Code,
      Theta = model$theta[, topic_number],
      Income_Group = factor(paste("Income", .x), levels = paste("Income", 1:4)),
      stringsAsFactors = FALSE
    )
  }) 
}

# 2. Get all topics data
all_topics_data <- map_dfr(1:5, ~{
  prepare_topic_data(.x) %>% 
    mutate(Topic = factor(paste("Topic", .x)))
})

# 3. Calculate topic-specific weights
topic_weights <- all_topics_data %>%
  group_by(Topic, Year, Income_Group) %>%
  summarise(
    n_countries = n_distinct(ISO_Code),
    .groups = "drop"
  ) %>%
  group_by(Topic, Year) %>%
  mutate(weight = n_countries / sum(n_countries)) %>%
  ungroup()

# 4. Join weights and calculate weighted statistics
final_results <- all_topics_data %>%
  left_join(topic_weights, by = c("Topic", "Year", "Income_Group")) %>%
  group_by(Topic, Year) %>%
  summarise(
    weighted_mean = weighted.mean(Theta, w = weight),
    weighted_ci_lower = quantile(Theta * weight, 0.025),
    weighted_ci_upper = quantile(Theta * weight, 0.975),
    n_countries = sum(n_countries),
    .groups = "drop"
  )
```

